---
title: "Reproduction code for Castanho Silva, Vegetti, and Littvay 2017"
author: "Bruno Castanho Silva, Federico Vegetti, and Levente Littvay"
date: "September 1, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This file contains reproduction codes for the results presented in Castanho Silva, Bruno, Federico Vegetti, and Levente Littvay. 2017. The Elite is up to Something: Exploring the Relation Between Populism and Belief in Conspiracies. Swiss Political Science Review, doi: 10.1111/spsr.12270: http://onlinelibrary.wiley.com/doi/10.1111/spsr.12270/full.

Please find the respective codebooks here:

2014: https://www.dropbox.com/s/mhdg8epfvpo9c1v/polberg_0114_mturk_codebook_v1.1.3.pdf?dl=0

2015: https://www.dropbox.com/s/0nq3iivheohlxng/populism.survey.2015.codebook.v2.0.pdf?dl=0

## Preliminary steps:

Library and data:

```{r message=F}
library(lavaan)
data<-read.csv('mturk2014.csv')
pop<-read.csv('mturk2015.csv')
```

## Table 2


```{r}
model.cfa<-'
la.pop =~ pop2 + pop3 + pop4
la.ant =~ ant1 + ant2 + ant3 + ant4 + ant5 + ant6
la.c1 =~ cons1+ cons6 + cons11
la.c2 =~ cons2 + cons7 + cons12
la.c3 =~ cons3 + cons8 + cons13
la.c4 =~ cons4 + cons9 + cons14
la.c5 =~ cons5 + cons10 + cons15
'

fit.cfa<-cfa(model.cfa,data=data,fixed.x=F,std.ov=T,
             missing='fiml',mimic='Mplus',estimator='MLR')

inspect(fit.cfa, what='std')$psi
```

## Table 3

Regression results from Table 3 and factor loadings from Appendix A.

```{r cache=T}
model.regression<-'
la.pop =~ pop2 + pop3 + pop4
la.ant =~ ant1 + ant2 + ant3 + ant4 + ant5 + ant6
trust =~ trust1 + trust4 + trust5
la.c1 =~ cons1+ cons6 + cons11
la.c2 =~ cons2 + cons7 + cons12
la.c3 =~ cons3 + cons8 + cons13
la.c4 =~ cons4 + cons9 + cons14
la.c5 =~ cons5 + cons10 + cons15
la.pop ~ la.c1 + la.c2 + la.c3 + la.c4 + la.c5 + edu + gender + lib + age + white + income + trust
la.ant ~ la.c1 + la.c2 + la.c3 + la.c4 + la.c5 + edu + gender + lib + age + white + income + trust
'

reg.fit<-sem(model.regression, data=data, fixed.x=F,std.ov=T,missing='fiml',mimic='Mplus',estimator='MLR')

summary(reg.fit, fit.measures=T,standardized=T)
```

## Table 4

```{r}
model.cfa.2<-'
people =~ genwill17 + simple8 + genwill3
antiel =~ antiel23 + rwpop8 + antiel21
manich =~ manich15 + manich13 + manich14
consp =~ cmq5 + cmq2 + cmq3 + cmq4 + cmq1
cmq5 ~~ cmq4
'
fit.cfa.2<-cfa(model.cfa.2,data=pop, fixed.x=F,std.ov=T,missing='fiml',mimic='Mplus',estimator='MLR')

inspect(fit.cfa.2, what='std')$psi
```

## Table 5

Regression results from table 5 and factor loadings from Appendix B.

```{r cache=T}
model.2<-'
people =~ genwill17 + simple8 + genwill3
antiel =~ antiel23 + rwpop8 + antiel21
manich =~ manich15 + manich13 + manich14
consp =~ cmq5 + cmq2 + cmq3 + cmq4 + cmq1
trust =~ cgov + cparty + ccongr
manich ~ consp + edu + white + female + age + income + lib + trust
people ~ consp + edu + white + female + age + income + lib + trust
antiel ~ consp + edu + white + female + age + income + lib + trust
cmq5 ~~ cmq4
'
fit.sem2<-sem(model=model.2,data=pop,missing = 'fiml',estimator='MLR',mimic='Mplus',std.ov=T)

summary(fit.sem2,fit.measures=T,standardized=T)
```
